Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Rewording manual constraints
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1620 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: 
supporting for the syntax-augmented machine translation (SAMT) grammar,
supporting mannual constraints in the input to constrain the decoding,  
lattice parsing for dealing with input uncertainty,
semiring parsing for unified dynamic programming, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees and hypergraphs, 
and a unified pipeline for MT experiments.
\end{abstract}

@@

The toolkit has been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
supporting for syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
supporting manual constraints in the input to constrain the decoding \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

\section{Manual Constraints on the Input}
\todo{anni}

>>>>

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: 
supporting for the syntax-augmented machine translation (SAMT) grammar,
support for external modules to posit translations for spans in the input sentence that constrain decoding,  
lattice parsing for dealing with input uncertainty,
semiring parsing for unified dynamic programming, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees and hypergraphs, 
and a unified pipeline for MT experiments.
\end{abstract}

@@

The toolkit has been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
support for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

\section{Specifying Constraints on the Rules}
\todo{anni}
